dispRity manual

### 2017-05-29 doc/dispRity-manual.Rmd
Updated manual

```{r, fig.width=6, fig.height=6}
## Setting the random seed for repeatability
set.seed(123)

@@

This

```{r}
# dispRity.through.time()
```

@@

```{r}
# dispRity.per.group()
```

@@

>>>>

```{r, fig.width=7, fig.height=7}
## Setting the random seed for repeatability
set.seed(123)

@@

One of the functions of the package is to look at how disparity changes through time.
This function (and the following one) are the two most straight forward, they analysis the ordinated data in a pipelined way using a lot of default parameters.

For disparity through time analysis, you will need:

  * An ordinated matrix (we covered that above)
  * A phylogenetic tree: this must be a `phylo` object (from the `ape` package) and needs a `root.time` element. To give your tree a root time, you can simply do `my_tree$root.time <- my_age`.
  * A required number of time subsamples (here 3)
  * Your definition of disparity (here the sum of variances)

Note that in the following example, the matrix and the tree comes from the previous sections

```{r}
## Measuring disparity through time
disparity_data <- dispRity.through.time(BeckLee_mat50, BeckLee_tree,
                                        time = 3, metric = c(sum, variances))
```

When display our disparity data, we can now have information on the operations done to the matrix:

```{r}
## Printing what's in the disparity data
disparity_data
```
Indeed, we asked for three subsamples (evenly spread across the age of the tree), the data was bootstrapped 100 times and the metric used was the sum of variances.

We can now analyse this data by summarising and plotting it or performing some statistical tests on it (e.g. a simple `aov`):

```{r, fig.width=7, fig.height=7}
## Summarising the measurements
summary(disparity_data)

## Plotting the results
plot(disparity_data)

## Testing for an eventual difference between the time bins
disp_aov <- test.dispRity(disparity_data, test = aov, comparisons = "all")
summary(disp_aov)
```

Please refer to the specific tutorials below for (much!) more information on the nuts and bolts of the package.
You can also directly explore the specific functions manuals within R and navigate to they're related functions.

@@

One other typical analysis done with disparity is to look at the difference in disparity between several groups.

```{r}
## Creating the two groups as a list
mammal_groups <- list("crown" = c(16, 19:41, 45:50),
                      "stem" = c(1:15, 17:18, 42:44))

## Measuring disparity for each group
disparity_data <- dispRity.per.group(BeckLee_mat50, group = mammal_groups,
                                     metric = c(sum, variances))
```

Similarly as above, we can display information about both groups by simply calling it and then summarising the data (and plotting it!) and performing a statistical test to compare both groups (here a Wilcoxon test).

```{r, fig.width=7, fig.height=7}
## Printing what's in the disparity data
disparity_data

## Summarising the measurements
summary(disparity_data)

## Plotting the results
plot(disparity_data)

## Testing for an eventual difference between the groups
test.dispRity(disparity_data, test = wilcox.test, details = TRUE)

```

@@

## Bootstraps and rarefactions

## Time slicing

## Disparity metrics

## Plotting `dispRity` data

## Testing disparity hypothesis

## Disparity as a distribution

## Ecological study
